Implementing Change in Multi-paradigm Environments, a Case Study

### 2015-02-25 rmtw/a3/latex8.tex
xd
Changed threats to subsection under meth
Changes have been made

\overfullrule=2cm

@@

In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK. The study focused mostly on how the companies perform SPI and how effective their efforts were. The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.

@@

@@

@@

@@

@@

\SubSection{Data Analysis}
Data analysis of the interviews was completed in tandem with the data gathering phase. This was performed so that we could iteratively improve upon the data collection process. The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions. The interviews were analysed by manually reading and comparing answers between the respondents. Spreadsheets and tables were used to provide an overview of the results.

@@

\Section{Threats to Validity}

@@

\Section{Acknowledgements}
John had the main responsibility for sections 1 \& 2. William had the main responsibility for section 3. Section 4 and the interview questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.

@@

>>>>

@@

In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK. The study focused mostly on how the companies perform SPI and how effective their efforts were. The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding. --Change this to something useful?

@@

Mention criteria for pool of companies and clarify this a bit.
Rephrase the first two sentences

@@

#Clarifications on terms for MC/MDD

@@

3-3 Clarify how and what department is chosen, i.e. we only looked at EPG so don't make it sound like we did something else.

@@

#Bit more explanation for distinction between the roles and phrasing of the sentence

@@

\SubSection{Data Analysis}
#Add initially, tandem implies something else, add more detail here, explaining the analysis more, how the data is constructed, what tools are used and how it's processed. i.e. more detail about spreadsheets and tables.

Data analysis of the interviews was completed in tandem with the data gathering phase. This was performed so that we could iteratively improve upon the data collection process. The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions. The interviews were analysed by manually reading and comparing answers between the respondents. Spreadsheets and tables were used to provide an overview of the results.

@@

\SubSection{Threats to Validity}
#Revisit the triangulation period

@@

\Section{Acknowledgements}
John had the main responsibility for sections 1, 2. William had the main responsibility for section 3. Section 3.6 and the interview questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.

@@

%Recap question, describe the interview and questions
%Timeline could be created and added
